Improving the portuguese hyphenation rules

### 2024-07-01 article/limitations.tex
fix #52

    \item [Foreignness\label{foreignness}] There is a group of words %20 words 
	in the corpus that are terminologies or words incorporated into the 
	Portuguese language without full phonological adaptation, such as 
	\emph{darwinismo}, \emph{quilowatt}, and \emph{esfiha}. The lack of
	adaptation makes the phonological pattern very specific to the word,
	making it impossible to incorporate their cases \TeX{}'s rules alongside the
	other rules. The solution is to add them to the exception word list.

>>>>

    \item [Foreignness\label{foreignness}] There is a group of words in the
      corpus that are terminologies or words incorporated into the Portuguese
      language without full phonological adaptation, such as \emph{darwinismo},
      \emph{quilowatt}, and \emph{esfiha}. This lack of adaptation results in
      phonological patterns that are highly specific to each word, making it
      impractical to integrate their cases into \TeX{}'s rules alongside other
      rules. Especially for words like \emph{farquhar} and \emph{qubit}, which
      are not only foreign but also rarely used in the language, the solution
      is to add them to the exception word list.
